\chapter{Abstract}


\begin{english} %switch to English language rules

Regression models are an important tool in the field of data analysis. They are used for the statistical prediction of values. Visualizations are required, to validate these developed regression models. The visualizations are either used from an existing library or developed specifically for the use case. However, they often come with deficits. These involve hard integration into projects or low functionality and missing interactivity of the diagrams. Fixing these issues requires a new library for the visualization of regression models. The goal of this thesis is the development of such a library. It should include four specific diagrams. These are line chart, scatter plot, bubble chart and partial dependency plot. Line chart and scatter plot are commonly used diagrams which allows for a simple introduction into the development. Bubble chart and the partial dependence plot, on the other hand, offer rich interactivity to the users. Their implementation offers insights on the difficulties of creating complex diagrams. The development is based on four different libraries: matplotlib, pandas, and scikit-learn. How these libraries can be used for the development of diagrams is also outlined within the. The result of the thesis, is the presentation of the final library. The included diagrams allow for complex, interactive analysis, which are not possible with currently available libraries. This removes the requirement for a custom, time intensive implementation. The end of the thesis represents a possible outlook onto further extensions of the library.

\end{english}

